---
title: "lab 8"
author: "Alissa Patterson"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
```

# read in 

```{r}
homes <- read_csv(here("slo_homes (1).csv"))
```
### create a subset with 4 cities

Task: create a subset (called homes_subset) that only contains observations wehre the city is:

"San Luis Obsipo"
"Atascadero"
"Arroyo Grande"
"Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### Create a summary table that has the mean and standrd deviation of home prices grouped by city and sale status 

```{r}
homes_subset %>%
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price),
            sd_price = sd(Price),
            mean_sqft = mean(SqFt))
  
```
Explore the relationship between square footage and home price in scatterplot 

```{r}
ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
geom_point() +
  geom_smooth(method = 'lm')
```
### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home Price

create 2 different permutations of this model:

1. Price ~ City, Bedrooms, Bathrooms, SqFt, and Status (lm1)
2. Price ~ City, SqFt, Status (lm2)
3. Try another one (lm3)

```{r}
lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)

lm2 <- lm(Price ~ SqFt, data = homes_subset)

lm3 <- lm(Price ~ SqFt, data = homes_subset)

# If I wanted SLO to be the reference level:
# Use fct_relevel to specify a new reference level 

new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo"))

lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)

summary(lm_slo)

```
Make a subset called homes_quant that only contains variables from Price through SqFt

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_cor <- cor(homes_quant)
```



```{r}
AIC(lm1)
AIC(lm2)
```

### Use modelsummary() 

```{r}
modelsummary(list(lm1, lm2, lm3))
```
```{r}
plot(lm1)
```
```{r}
home_predictions <- augment(lm1)
```
# Make a histogram of the residuals form this model (lm1)

```{r}
ggplot(data = home_predictions, aes(x = .resid))
geom_histogram()
```

# BRANCHES ARE COOL